\documentclass{resume}
\usepackage[dvipsnames,svgnames,x11names,hyperref]{xcolor}
\usepackage{tikz}
% \usepackage{natbib}
\usetikzlibrary{decorations.pathmorphing}
\usepackage[colorlinks = true,
            linkcolor = green,
            urlcolor  = OliveGreen,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage[utf8]{inputenc}

\renewcommand\refname{Publications}

\def\FormatName#1{%
  \def\myname{Emma Strubell}%
  \edef\name{#1}%
  \ifx\name\myname
    \textbf{#1}%
  \else
    #1%
  \fi
}

\begin{document}

\begin{center}
\textsc{\huge{Emma Strubell}}\\
\tikz \draw [-,
% OliveGreen,
line join=round,
decorate, decoration={
    coil,
    segment length=8,
    amplitude=.5,
}]  (0,0) -- (8,0); \\
\smallskip
\small{strubell@cs.umass.edu}\\
\small{\href{http://cs.umass.edu/~strubell}{http://cs.umass.edu/{\raise.17ex\hbox{$\scriptstyle\sim$}}strubell}}
\end{center}


\section{Education}

\stdtable{
 & \textbf{University of Massachusetts Amherst} \hfill 2012 --- 2019\\
 & Ph.D. in Computer Science \\
 & M.S. in Computer Science, 2012 --- 2015 \\ \\
 & \textbf{University of Maine} \hfill 2008 --- 2012\\
    & B.S. in Computer Science, \emph{summa cum laude}\\
    & Minor: Mathematics \& Statistics\\
}

\section{Research \& Professional Experience}

\employer
    {\textbf{Research Assistant}, \href{http://cics.umass.edu}{University of Massachusetts Amherst}}
    {September 2013 --- present}
    {Advisor: \href{http://cs.umass.edu/~mccallum}{Andrew McCallum}} {http://cics.umass.edu}
\\ \\ \\
\employer
    {\textbf{Research Intern}, \href{https://ai.google/research/teams/language/}{Google AI Language}}
    {May --- August 2017}
    {Supervisors: \href{https://ai.google/research/people/DanielAndor}{Daniel Andor}, \href{https://ai.google/research/people/DavidWeiss}{David Weiss}}
\\ \\ \\ \\
\employer
    {\textbf{Research Intern}, \href{https://developer.amazon.com/alexa/science}{Amazon Alexa Science}}
    {June --- September 2016}
    {Supervisor: \href{http://www.tkollar.com/}{Thomas Kollar}}
\\ \\ \\ \\
\employer
{\textbf{Research Assistant}, \href{http://cics.umass.edu}{University of Massachusetts Amherst}}
{September 2012 --- May 2013}
{Advisor: \href{http://cs.umass.edu/~hava}{Hava Siegelmann}} {http://cics.umass.edu}
\\ \\ \\
\employer
{\textbf{Research Assistant}, \href{http://umaine.edu/cs/}{University of Maine}}
{May 2011 --- August 2012}
{Advisor: \href{http://www.math.umaine.edu/~hiebeler/}{David Hiebeler}} {http://cics.umass.edu}

\section{Awards}
\begin{itemize}
\item {Best Long Paper Award, EMNLP 2018}
\item {IBM PhD Fellowship Award, 2017--2018}
\item {Yahoo Outstanding Accomplishments in Search and Mining Award, 2016}
\item {Grace Hopper Conference Scholarship Grant (21\% acceptance), 2015}
\item {EMC CRA-W Grad Cohort Scholarship Award, 2015}
\item {Outstanding Paper Award, ACL 2015}
\item {UMaine College of Liberal Arts \& Sciences Undergraduate Research Fellowship, 2011--2012}
\end{itemize}
\clearpage

\nocite{*}
\bibliography{publications}
\bibliographystyle{unsrt_bold}
% \begin{enumerate}

% \item Eunsol Choi*, He He*, {\bfseries Mohit Iyyer}*, Mark Yatskar*, Wen-tau Yih, Yejin Choi, Percy Liang, Luke Zettlemoyer.
%  \href{https://arxiv.org/abs/1808.07036}{QuAC: Question Answering in Context.} \emph{EMNLP} 2018. 

% \section{Talks}
% \begin{itemize}
% \item November 2018: CMU LTI Colloquium
% \item March 2018: UMass CS Women Lunch
% \end{itemize}

\section{Teaching}
\employer
   {\textbf{Team Mentor}, \href{http://cics.umass.edu}{University of Massachusetts Amherst}}
   {January --- May 2017, 2018}
   {Course: \href{http://ds.cs.umass.edu/industry-mentorship-program}{MS Industry Mentorship Program} with \href{https://www.chanzuckerberg.com/science/projects-meta}{Chan Zuckerberg Initiative}} {http://ds.cs.umass.edu/}
\\ \\ \\
\employer
    {\textbf{Guest Lecturer}, \href{http://cics.umass.edu}{University of Massachusetts Amherst}}
    {October 2017}
    {Course: \href{https://compsci682.github.io/syllabus.html}{Neural Networks} with \href{http://cs.umass.edu/~elm}{Erik Learned-Miller}} {http://cics.umass.edu}
\\ \\ \\ 
\employer
    {\textbf{Teaching Assistant}, \href{http://cics.umass.edu}{University of Massachusetts Amherst}}
    {September --- December 2012}
    {Course: \href{https://people.cs.umass.edu/~immerman/cs250/syllabus.html}{Introduction to Computation} with \href{http://cs.umass.edu/~immerman}{Neil Immerman}} {http://cics.umass.edu}
\\ \\ \\ 
\employer
    {\textbf{Teaching Assistant}, \href{https://umaine.edu/cs/}{University of Maine}}
    {January --- May 2012}
    {Course: Automata, Computability and Languages with Larry Latour} {https://umaine.edu/cs/}

\section{Service \& Outreach}
\begin{itemize}
\item Panelist, \emph{Succeeding in Graduate School: Advice from Outstanding Students in the Sciences}, 2017. 
\item Co-organizer and mentor, Cross-cultural Graduate Peer Mentoring Program (\$1000 Welcoming the World to Amherst Grant), 2017
\item Co-organizer, CS Women Travel Grant Program (\$5000 Women for UMass Grant), 2016--2017.
\item Co-organizer, CS Women Technical Skills Workshops (\$1000 NCWIT Seed Grant), 2015--2016.
\item Co-chair and treasurer, UMass CS Women, 2015--2017.
\item Senator, UMass Graduate Student Senate, 2014--2015.
\item Mentor, Girls Inc. Eureka! Workshop (Programming in Scratch), 2014, 2015.
\item Mentor, CAITE Women in Engineering \& Computing Career Day, 2013, 2015.
\item Steward, UMass Graduate Employee Organization (UAW 2322), 2013--2014.
\item Reviewer, NCWIT Aspirations in Computing Scholarship, 2013, 2014.
\item Panelist, \emph{UMaine Outstanding Students in the College of Liberal Arts and Sciences}, 2012. 
\item Program Committees: ACL 2017, 2018 (top reviewer); EMNLP 2015, 2017, 2018; SCiL 2019; ICWSM 2019; PLDI 2016.
\item Student volunteer, NAACL 2018.
\end{itemize}

\section{Professional Development}
\begin{itemize}
\item WW2A Cross-Cultural Mentoring Workshop, 2016.
\item \href{https://www.cirtl.net/courses/261}{CIRTL Research Mentor Training Course}, 2016.
\item UMass OPD Workshop on Engaging Students in Effective Discussions and Active Learning, 2015.
\end{itemize}

\section{Mentoring}
\begin{itemize}
\item Juhi Shah (2018). Undergraduate independent study at Mt. Holyoke College. \emph{Automatically detecting fake news using neural networks}.
\item Ananya Ganesh (2018). Masters project at University of Massachusetts Amherst. \emph{Improved representation learning for semantic role labeling}.
\item Sheshera Mysore (2017). Masters project at University of Massachusetts Amherst. \emph{Kernelized matrix completion for predicate-argument schema induction and extraction}.
\item Aditya Shastry (2017). Masters project at University of Massachusetts Amherst. \emph{Automatic header field extraction from research articles}.
\item Molly McMahon (2016). Masters project at University of Massachusetts Amherst. \emph{Automatic citation field extraction from research articles}
\item Abdurrahman Munir (2016). Louis Stokes Alliance for Minority Participation (LSAMP) undergraduate research fellow at University of Massachusetts Amherst. \emph{Character-level modeling for Arabic tokenization and named entity recognition}.
\item Katherine Silverstein (2015). Undergraduate independent study at University of Massachusetts Amherst. \emph{Fast and accurate models for named entity recognition}.
\end{itemize}


\end{document}